DATA 621 Homework #2

### 2019-10-06 hw2/HW2.Rmd
Added pROC Output
Work on ROC

>>>>

## pROC Output

```{r}
par(pty = "s")
roc(df[[actual]], df[[predicted]], plot = TRUE, legacy.axes = TRUE, percent = TRUE, print.auc = TRUE)
par(pty = "m")
```

## Our ROC Curve

```{r}
# This is for testing only
roc_curve(df, actual, probability) %>%
  kable() %>%
  kable_styling()
```

```{r}
df$test <- ifelse(df[[probability]] > 0.02, 1, 0)
confusion_matrix(df, actual, "test")
```

```{r}
df$test <- ifelse(df[[probability]] > 0.95, 1, 0)
confusion_matrix(df, actual, "test")
```
